### 2019-08-14 paper_03_toy_model/article.tex
Formatting equations

The toy model equations can be expressed as three coupled equations for $ \Psi $, $ \chi $ and $ \theta $. Unfortunately, we have found no elegant way in which they can be expressed in vector notation, why we write them as
\begin{eqnarray} \label{PsiEq}
\frac{\partial{\Psi_{ii}}}{\partial t} +\epsilon_{ijk}e_k \Psi_i \Psi_{jll} + \Psi_{ii} \chi_{jj} - \Psi_{ij} \chi_{ij} = -f \chi_{ii} + (-1)^{p+1} \nu_p \nabla^{2p} \Psi_{ii} \, , \\ \label{ChiEq}
\frac{\partial{\chi_{ii}}}{\partial t} +\epsilon_{ijk}e_k (\Psi_i \chi_{jll} - \Psi_{jl} \chi_{il}) + \Psi_{ij} \Psi_{ij} - \Psi_{ii} \Psi_{jj} =  f \Psi_{ii} - c \theta_{ii} + (-1)^{p+1} \nu_p \nabla^{2p} \chi_{ii} \, , \\ \label{ThetaEq}
\frac{\partial{\theta}}{\partial t} + \epsilon_{ijk}e_k \Psi_i \theta_{j} = - c \chi_{ii} + (-1)^{p+1} \nu_p \nabla^{2p} \theta \, ,
\end{eqnarray}
where $ e_k $ is the vertical unit vector expressed in three-dimensional Cartesian tensor notation,  subscript $ i $  has the same meaning as $ {\partial }/{\partial x_i }$ when used on $ \Psi $,  $ \chi $ or $ \theta $ and repeated indices means summation.

>>>>

The toy model equations can be expressed as three coupled equations for $ \Psi $, $ \chi $ and $ \theta $. Unfortunately, we have found no elegant way in which they can be expressed in vector notation, why we write them as
\begin{align} \label{PsiEq}
&\frac{\partial{\Psi_{ii}}}{\partial t} +\epsilon_{ijk}e_k \Psi_i \Psi_{jll} + \Psi_{ii} \chi_{jj} - \Psi_{ij} \chi_{ij} = -f \chi_{ii} + (-1)^{p+1} \nu_p \nabla^{2p} \Psi_{ii} \, , \\ \label{ChiEq}
&\frac{\partial{\chi_{ii}}}{\partial t} +\epsilon_{ijk}e_k (\Psi_i \chi_{jll} -
\Psi_{jl} \chi_{il}) + \Psi_{ij} \Psi_{ij} - \Psi_{ii} \Psi_{jj} \nonumber\\
&\quad=  f \Psi_{ii} - c \theta_{ii} + (-1)^{p+1} \nu_p \nabla^{2p} \chi_{ii} \, , \\ \label{ThetaEq}
&\frac{\partial{\theta}}{\partial t} + \epsilon_{ijk}e_k \Psi_i \theta_{j} = - c \chi_{ii} + (-1)^{p+1} \nu_p \nabla^{2p} \theta \, ,
\end{align}
where $ e_k $ is the vertical unit vector expressed in three-dimensional Cartesian tensor notation,  subscript $ i $  has the same meaning as $ {\partial }/{\partial x_i }$ when used on $ \Psi $,  $ \chi $ or $ \theta $ and repeated indices means summation.
